---
title: "COMPUTERS"
author: "Presented by Djamal Toe and Chahid El Hammouti"
institute: "National School for Statistic and Data Analysis"
date: "`r Sys.Date()`"
format:
  revealjs:
    transition-speed: fast
    aspect_ratio: "16:9"
    margin: 0.05
    fig_caption: yes
    center: true
    logo: "images/LLOGO.png"
    footer: "English classes with Milonnet"
    css: style.css
fig_caption: yes
toc: true
toc-expand: false
toc-depth: 1
toc-title: "Table of contents"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
capTabNo = 1; capFigNo = 1;
capTab = function(x){
 
    x = paste0("Table ",capTabNo," : ",x)
    capTabNo <<- capTabNo + 1
 x
}

capFig = function(x){
 
    x = paste0("","","",x)
    capFigNo <<- capFigNo + 1
    x
}

repeated_capFig = function(x){
  x = paste0(paste0(paste0("Figure ", capFigNo), ""), x)
  x
}
```

```{r}
packages_ <- c("ggplot2", "dplyr","readxl","cowplot")

for (pkg in packages_) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg, dependencies = T)
  }
  library(pkg, character.only = TRUE)
}
```

# Introduction

## News Stories

::: {.fragment .highlight-red}
- News paper : The Guardian
:::

::: {.fragment .highlight-blue}
- Title : IBM unveils new quantum computing chip to explore news frontiers of science
:::

## Computers ?

. . .

:::: {.columns}


::: {.column width="48%"}
```{r, fig.align='center', out.width='90%', out.height="90%"}
fig.path <- paste0(getwd(),"/images/")
def.img <- paste0(fig.path,"definition.jpg")
oldSys.img <- paste0(fig.path,"old_system.jpg")
newSys.img <- paste0(fig.path,"new_system.jpg")
definition <- ggdraw() + draw_image(image = def.img)
definition
```

::: {.fragment .highlight-blue}
::: {data-id="def" style="background: #fff; width: 100%; height: 100%; font-size: 0.9em;"}
Programmable information processus system
:::
:::

:::

::: {.column width="48%"}

::::{.rows}

:::{.row heigth="40%"}
```{r, fig.align='center', out.width='80%', out.height="60%"}
oldSys <- ggdraw() + draw_image(image = oldSys.img)
oldSys
```
:::

:::{.row heigth="10%"}
::: {.fragment .highlight-blue}
::: {data-id="evolution" style="background: #fff; width: 100%; height: 100%; font-size: 0.7em;"}
Old System ===>> New System
:::
:::
:::

:::{.row heigth="40%"}
```{r, fig.align='center', out.width='80%', out.height="60%"}
newSys <- ggdraw() + draw_image(image = newSys.img)
newSys
```
:::



::::
:::

::::

## Quantum computing chips ?

::: {.fragment .highlight-blue}
* Use qbits to perform computing instead of using simply bits
:::

* <https://www.theguardian.com/technology/2023/dec/04/ibm-quantum-computer-heron>

# Challenges

## Avantages 

-   Solve many domains problems
-   Blabla bla

## Incoveniants

-   Instabilité et décohérance quantique : sensibles aux pertubations, variation de temperature, bruit
-   infrastructure couteuse et contraignante

## Words explanation

* Silicon-based computers : 

. . .

* Quantum computing chip : a procesor which uses qbits to perform computing instead of using simply bits

. . .

* Supercomputers : Computers with big Computational ability/ hight performance

## Words explanation

* Artificial Intelligence : An informatic system which is able to carry out some tasks which normally need human intelligence

. . .

* Computational ability : Computing capacities

# Conclusison