---
title: "COMPUTERS"
author: "Presented by Djamal Toe and Chahid El Hammouti"
institute: "National School for Statistic and Data Analysis"
date: "`r Sys.Date()`"
format:
  revealjs:
    transition-speed: fast
    aspect_ratio: "16:9"
    margin: 0.02
    fig_caption: yes
    center: true
    logo: "images/LLOGO.png"
    footer: "English classes with Milonnet"
    css: style.css
fig_caption: yes
toc: true
toc-expand: false
toc-depth: 1
toc-title: "Table of contents"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r}
capTabNo = 1; capFigNo = 1;
capTab = function(x){
 
    x = paste0("Table ",capTabNo," : ",x)
    capTabNo <<- capTabNo + 1
 x
}

capFig = function(x){
 
    x = paste0("","","",x)
    capFigNo <<- capFigNo + 1
    x
}

repeated_capFig = function(x){
  x = paste0(paste0(paste0("Figure ", capFigNo), ""), x)
  x
}
```

```{r}
packages_ <- c("ggplot2", "dplyr","readxl","cowplot")

for (pkg in packages_) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg, dependencies = T)
  }
  library(pkg, character.only = TRUE)
}
```

# Introduction

## News Stories

::: {.fragment .highlight-red}
- News paper : The Guardian
:::

::: {.fragment .highlight-blue}
- Title : IBM unveils new quantum computing chip to explore news frontiers of science
:::

## Computers ?

. . .

:::: {.columns}


::: {.column width="48%"}
```{r, fig.align='center', out.width='90%', out.height="90%"}
fig.path <- paste0(getwd(),"/images/")
def.img <- paste0(fig.path,"definition.jpg")
oldSys.img <- paste0(fig.path,"old_system.jpg")
newSys.img <- paste0(fig.path,"new_system.jpg")
definition <- ggdraw() + draw_image(image = def.img)
definition
```

::: {.fragment .highlight-blue}
::: {data-id="def" style="background: #fff; width: 100%; height: 100%; font-size: 0.9em;"}
Programmable information processing system
:::
:::

:::

::: {.column width="48%"}

::::{.rows}

:::{.row heigth="40%"}
```{r, fig.align='center', out.width='80%', out.height="60%"}
oldSys <- ggdraw() + draw_image(image = oldSys.img)
oldSys
```
:::

:::{.row heigth="10%"}
::: {.fragment .highlight-blue}
::: {data-id="evolution" style="background: #fff; width: 100%; height: 100%; font-size: 0.7em;"}
Old System ===>> New System
:::
:::
:::

:::{.row heigth="40%"}
```{r, fig.align='center', out.width='80%', out.height="60%"}
newSys <- ggdraw() + draw_image(image = newSys.img)
newSys
```
:::



::::
:::

::::

## Quantum computing chips ?

::: {.fragment .highlight-blue}
* Use qbits to perform computing instead of using simply bits
:::

```{r fig.align='center', out.height="70%", out.width="80%"}
library(ggplot2)
data <- data.frame(
  System = c("Classical", "Quantum"),
  Performance = c(10, 100)
)
ggplot(data, aes(x = System, y = Performance, fill = System)) +
  geom_bar(stat = "identity") +
  labs(title = "Performance Comparison", y = "Performance Units") +
  theme_minimal()
```


# Challenges

## Avantages 

::: {.fragment .highlight-blue}
**Solve many domains problems**
:::

```{r, fig.align='center', out.height="80%", out.width="85%"}
advantages <- data.frame(
  Category = c("Speed", "Efficiency", "Problem Solving"),
  Score = c(9, 8, 7)
)

advantage_plot <- ggplot(advantages, aes(x = Category, y = Score, fill = Category)) +
  geom_bar(stat = "identity", width = 0.7, show.legend = FALSE) +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Advantages of Quantum Computing", y = "Score", x = "") +
  theme_minimal(base_size = 14)
advantage_plot
```


## Challenges

```{r fig.align='center', out.height="75%", out.width="85%"}
challenges <- data.frame(
  Category = c("Cost", "Instability", "Environment"),
  Score = c(8, 9, 7)
)

challenge_plot <- ggplot(challenges, aes(x = Category, y = Score, fill = Category)) +
  geom_bar(stat = "identity", width = 0.7, show.legend = FALSE) +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Challenges of Quantum Computing", y = "Score", x = "") +
  theme_minimal(base_size = 14)

challenge_plot
```

::: {.fragment .highlight-red}
**Expensive, unstable, needs controlled environment**
:::

# Conclusison

## Summary

* Quantum computers are promising 

* Challenges remain for full adoption

* <https://www.theguardian.com/technology/2023/dec/04/ibm-quantum-computer-heron>

## Questions ?

::: {data-id="thx" style="background: #fff; color: light-blue; text-align: center; font-family: times new roman ; width: 100%; height: 100%; font-size: 1.5em;"}
!!! THANK YOU FOR YOUR ATTENTION
:::

```{r, fig.align='center', out.width='80%', out.height="60%"}
quest.img <- paste0(fig.path,"interrogation2.png")
questions <- ggdraw() + draw_image(image = quest.img)
questions
```

